Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case

### 2019-01-19 ICML-submission/title-and-abstract.tex
Update title-and-abstract.tex
Changed the title

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Online Multiclass Linear Classification with Bandit Feedback}

\twocolumn[
\icmltitle{Online Multiclass Linear Classification with Bandit Feedback}

>>>>

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case}

\twocolumn[
\icmltitle{Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case}
